### 2021-09-29 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@defa89250558fde8b6679c4f29cd9ff592e3768b 🚀

So as to simplify the notation of the following section, I will
introduce a series of new variables. Let \(A = |E_c|\) be the number of
links that are identical between networks; \(S = |E_{sn} \cup E_{sm}|\)
be the number of links that are not shared, but only involve shared
species (\emph{i.e.} links from \(\mathcal{M}\cup\mathcal{N}\)
established between species from \(\mathcal{M}\cap\mathcal{N}\)); and
\(U = |E_{un} \cup E_{um}|\) the number of links that are not shared,
and involve at least one unique species. Adopting the perspective
developed in the previous section, wherein networks are sets and the
measures of \(\beta\)-diversity operates on these sets, highlights the
conceptual issue in the Fründ (2021) alternative normalization: they are
using components of the networks that are \emph{not} part of the
networks being compared.

There are two important points to note here. First, the number or
proportion of species that are shared is not involved in the
calculation. Second, the connectance of either network is not involved
in the calculation. That all links counted in \emph{e.g.} \(U\) come
from \(\mathcal{M}\), or that they are evenly distributed between
\(\mathcal{M}\) and \(\mathcal{N}\), has no impact on the result. This
is a desirable property of the approach: whatever quantitative value of
the components of dissimilarity can be interpreted in the light of the
connectance and species turnover \emph{without} any risk of circularity.
Therefore the argument of Fründ (2021), whereby the \(\beta_{os}\)
component should decrease with turnover, and be invariant to
connectance, does not hold: the very point of the approach is to provide
measures that can be interpreted in the light of connectance and species
turnover.

@@

>>>>

So as to simplify the notation of the following section, I will
introduce a series of new variables. Let \(C = |E_c|\) be the number of
links that are identical between networks (as a mnemonic, \(C\) stands
for ``common''); \(R = |E_{sn} \cup E_{sm}|\) be the number of links
that are not shared, but only involve shared species (\emph{i.e.} links
from \(\mathcal{M}\cup\mathcal{N}\) established between species from
\(\mathcal{M}\cap\mathcal{N}\); as a mnemonic, \(R\) stands for
``rewired''); and \(T = |E_{un} \cup E_{um}|\) the number of links that
are not shared, and involve at least one unique species (as a mnemonic,
\(T\) stands for ``turnover'').

There are two important points to note here. First, as mentionned
earlier, the number or proportion of species that are shared is not
involved in the calculation. Second, the connectance of either network
is not involved in the calculation. That all links counted in
\emph{e.g.} \(U\) come from \(\mathcal{M}\), or that they are evenly
distributed between \(\mathcal{M}\) and \(\mathcal{N}\), has no impact
on the result. This is a desirable property of the approach: whatever
quantitative value of the components of dissimilarity can be interpreted
in the light of the connectance and species turnover \emph{without} any
risk of circularity; indeed, I present a numerical experiment where
connectance varies independently later in this manuscript.

@@

\textbf{TK} Therefore the argument of Fründ (2021), whereby the
\(\beta_{os}\) component should decrease with turnover, and be invariant
to connectance, does not hold: the very point of the approach is to
provide measures that can be interpreted in the light of connectance and
species turnover.

\textbf{TK} Adopting the perspective developed in the previous section,
wherein networks are sets and the measures of \(\beta\)-diversity
operates on these sets, highlights the conceptual issue in the Fründ
(2021) alternative normalization: they are using components of the
networks that are \emph{not} part of the networks being compared.
